Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-09 papers/marlowe2019/paper.tex
Started on introduction.:wq

\begin{document}
%
\title{Marlowe: implementing and analysing financial contracts\thanks{Supported by IOHK.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Pablo {Lamela Seijas}\inst{1} \and
Alexander Nemish\inst{1} \and
David Smith\inst{1} \and
Simon Thompson\inst{1,2}\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas, A. Nemish, et al.}

@@

Intro
\section{Marlowe overview SJT}

@@

\section{Implementation of Marlowe on Cardano}

@@

\section{The Marlowe Playground}

>>>>

\begin{document}
%
\title{Marlowe: implementing and analysing financial contracts on blockchain}%\thanks{Supported by IOHK.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Pablo {Lamela Seijas}\inst{1} \and
Alexander Nemish\inst{1} \and
David Smith\inst{1} \and
Simon Thompson\inst{1,2}}%\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas, A. Nemish, et al.}

@@

Marlowe is a domain-specific language (DSL) for implementing financial contracts on blockchain: our initial target is Cardano, but it can be implemented on most DLT platforms, including Ethereum. Our DSL is embedded in Haskell, allowing users selectively to use aspects of Haskell -- typically definitions of constants and simple functions -- to express contracts more readably and succinctly. Marlowe was introduced in the paper~\cite{isola-marlowe}: Section \ref{sec:overview} here gives an overview of the language, and the changes made to it since the publication of that paper.

Marlowe is specified by a reference semantics for the language written in Haskell, thus giving us an \emph{executable} semantics for the language, which we can use in a number of ways. Obviously, we can interpret Marlowe contracts in Haskell itself, but we can also use that implementation, translated into Plutus~\cite{PlutusPlatform}, to interpret  Marlowe directly on the Cardano blockchain, as explained in Section \ref{sec:implementation}. Moreover, we can execute that semantics (translated into PureScript) directly in a browser to give an interactive simulation environment, the Meadow Playground, described in Section \ref{sec:playground}.

DSLs have a number of advantages over general purpose languages. TO COMPLETE.

\section{Marlowe overview}
\label{sec:overview}

, as well as the online simulation environment Meadow. Since publication we have revised the language design, and so we give a brief overview of the current (3.0) version of the language and its informal semantics.\footnote{The complete Marlowe project, including semantics and implementation, is available at \url{https://github.com/input-output-hk/marlowe}.} Meadow has been upgraded to the Marlowe Playground, and that is also introduced here.

@@

\section{Implementation of Marlowe on Cardano}
\label{sec:implementation}

@@

\section{The Marlowe Playground}
\label{sec:playground}
